Supplementary Information: Vulnerability of tree growth

### 2025-01-16 doc/manuscript.Rmd
couple of conceptual figs, bib and RMD files

## Figures
fig_DAG=1

# Read in files

```

@@

**Authors**  
```{r eval = TRUE, echo=FALSE, warning=FALSE, eval=F}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
team<- read.csv("display/authors.csv", stringsAsFactors = FALSE, check.names = FALSE)

ft <- flextable(team)
ft <- line_spacing(ft, space = 1, part = "all")
ft <- autofit(ft)
ft <- width(ft, 1, width = 1.75)
ft <- width(ft, 2, width = 1.75)
ft <- width(ft, 3, width = 3)
ft

```

@@

# Abstract {-}

@@

# Methods {-}

@@

>>>>

## Figures
fig_DAG <- 1

# Read in files
```

@@

**Authors**  
```{r eval = TRUE, echo=FALSE, warning=FALSE, eval=F}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
team <- read.csv("display/authors.csv", stringsAsFactors = FALSE, check.names = FALSE)

ft <- flextable(team)
ft <- line_spacing(ft, space = 1, part = "all")
ft <- autofit(ft)
ft <- width(ft, 1, width = 1.75)
ft <- width(ft, 2, width = 1.75)
ft <- width(ft, 3, width = 3)
ft
```

@@

# Summary {-}

- rationale  
- Methods  
- key Results   
- main conclusion

@@

# Materials and Methods {-}

@@

# Acknowledgements {-}

# Competing interests {-}

# Author contributions {-}

# Data availability
